ECCCos from the Black Box:\\ Faithful Explanations through\\ Energy-Constrained Conformal Counterfactuals

### 2023-09-26 paper/appendix.tex
done

In our experiments we always generate multiple counterfactuals for each model and generator. Each time the factual and target class is drawn randomly. For each generator and model we choose $n_f=100$ factuals for all of our synthetic and vision data. For tabular data we choose $n_f=25$ because larger values made grid search computationally prohibitive. For vision data, grid search was computationally prohibitve in any case, so hyperparameters were tuned manually. For all other datasets grid search was performed over different combinations of penalty strengths and optimizer steps sizes.

@@

Figures~\ref{fig:mnist-eccco-lenet} to~\ref{fig:mnist-eccco-jem-ens} show examples of counterfactuals for \textit{MNIST} generated by \textit{ECCCo+} for our different models. Original images are shown on the diagonal and the corresponding counterfactuals are plotted across rows. Figures~\ref{fig:mnist-revise-lenet} to~\ref{fig:mnist-revise-jem-ens} show the same examples but for \textit{REVISE}. Both counterfactual generators have access to the same optimizer. While the results for \textit{REVISE} look fairly poor here, we have observed better results for optizers with higher step sizes. Note that the seemingly poor performance by \textit{REVISE} upon visual inspection is not driven by a weak surrogate VAE: Figure~\ref{fig:vae-reg} shows image reconstructions generated by the VAE.

>>>>

In our experiments we always generate multiple counterfactuals for each model and generator. Each time the factual and target class is drawn randomly. For each generator and model we choose $n_f=100$ factuals for all of our synthetic and vision data. For tabular data we choose $n_f=25$ because larger values made grid search computationally prohibitive. For vision data, grid search was computationally prohibitve in any case, so hyperparameters were tuned manually. For all other datasets grid search was performed over different combinations of penalty strengths and optimizer steps sizes (details of which can be found in the code). To select the final hyperparameter setting we used the unfaithfulness metric as our criterion.

@@

Figures~\ref{fig:mnist-eccco-lenet} to~\ref{fig:mnist-eccco-jem-ens} show examples of counterfactuals for \textit{MNIST} generated by \textit{ECCCo+} for our different models. Original images are shown on the diagonal and the corresponding counterfactuals are plotted across rows. Figures~\ref{fig:mnist-revise-lenet} to~\ref{fig:mnist-revise-jem-ens} show the same examples but for \textit{REVISE}. Both counterfactual generators have access to the same optimizer. While the results for \textit{REVISE} look fairly poor here, we have observed better results for optizers with higher step sizes. Note that the seemingly poor performance by \textit{REVISE} upon visual inspection is not driven by a weak surrogate VAE: Figure~\ref{fig:vae-rec} shows image reconstructions generated by the VAE.
